Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-09 paper/EDA.qmd
Saving changes before rebase

## Confounding Variable: Age  
To reduce bias, we consider to control the experiment by controlling participant ages to be 18+. Hence in this study **age** acts as a **confounding variable**.
Participants will be categorized into three groups evenly to prevent bias created through age. 
The groups are as follows:
1. 18–34 years
2. 35–50 years
3. 50+ years

## Quantitative and Qualitative Variables 
In our study the quantitative and qualitative variables are as follows. 
Quantitative variables: Memory Game Scores, Memory Test Cards Scores 
Qualitative variables: Type of pain reliever, dosage level (low/high)

@@

1. The median scores for all drugs appear similar before treatment.
2. **Tramadol has a higher median** than other drugs both before and after treatment.
3. The **Placebo group has a slightly lower median score** compared to other drugs.
4. There is **one outlier in the Tramadol group before treatment**.
5. The (IQR) is **similar across all drug types**, though Tramadol sees a decrease in its IQR in the memory game scores after treatment.

>>>>

## Confounding Variable: Age  
To reduce bias, we consider to control the experiment by controlling participant ages to be 18+. Hence in this study **age** acts as a **confounding variable**.
Participants will be categorized into three groups evenly to prevent bias created through age. 
The groups are as follows:

1. 18–34 years
2. 35–50 years
3. 50+ years

## Quantitative and Qualitative Variables 
In our study the quantitative and qualitative variables are as follows:

1. Quantitative variables: Memory Game Scores, Memory Test Cards Scores 
2. Qualitative variables: Type of pain reliever, dosage level (low/high)

@@

1. The median scores for all drugs appear similar before treatment.
2. Tramadol has a higher median than other drugs both before and after treatment.
3. The Placebo group has a slightly lower median score compared to other drugs.
4. There is one outlier in the Tramadol group before treatment.
5. The (IQR) is **similar across all drug types**, though Tramadol sees a decrease in its IQR in the memory game scores after treatment.
